---
title: WordCloud
author: Shraddha Dubey
date: '2017-12-11'
slug: wordcloud
categories:
  - dplyr
  - ggplot2
tags:
  - wordcloud
---


To start working with Wordcloud and we need some words to create a wordcloud. 
I picked up one of the novels of Charles Dickens - Tale of Two Cities. The book is available to download from gutenbergr package.

Install and bring the following libraries to your workspace.


#### gutenbergr :  The gutenbergr package helps you download and process public domain works from the Project Gutenberg collection.

Metadata for all Project Gutenberg works as R datasets, so that they can be searched and filtered

gutenberg_download() :downloads one or more works from Project Gutenberg by ID  e.g., gutenberg_download(84) downloads the text of Frankenstein.

gutenberg_metadata :  contains information about each work, pairing Gutenberg ID with title, author, language, etc

gutenberg_authors : contains information about each author, such as aliases and birth/death year

gutenberg_subjects: contains pairings of works with Library of Congress subjects and topics



#### dplyr :The dplyr package helps with data manipulation challenges.

It provides simple "verbs", functions that correspond to the most common data manipulation tasks.It uses efficient backends, so we spend less time waiting for the computer.

Dplyr has following function for basic data manipulation:

filter() to select cases based on their values.

arrange() to reorder the cases.

select() and rename() to select variables based on their names.

mutate() and transmute() to add new variables that are functions of existing variables.

summarise() to condense multiple values to a single value.

sample_n() and sample_frac() to take random samples.



#### tidytext : Its used for Text mining and sentiment analysis along with other tools like dplye and ggplot2



#### wordcloud : A wordcloud is handy tool to highlight the most commonly cited words in a text using a quick visualization.

```{r,warning=FALSE,message=FALSE}
# download all the below mentioned packages first 
#using the following command 
#install.packages("package_name")
# install.packages("gutenbergr")
library(gutenbergr)
# install.packages("dplyr")
library(dplyr)
# install.packages("knitr")
library(knitr)
# install.packages("tidytext")
library(tidytext)
# install.packages("wordcloud")
library(wordcloud)
library(wordcloud2)
# install.packages("ggplot2")
library(ggplot2)
```


#### Download book

The first step towards making a wordcloud is getting text data. We are downloading 'A Tale of Two Cities' from gutenberg_works

```{r}

gutenberg_works(title=='A Tale of Two Cities')

# we can used the gutenberg_id to download
# the book into a dataframe

two_cities<-gutenberg_download(98)
two_cities[1:10,]

```



#### Unnest the words
As you can notice in the above section, the text column holds each sentence of the novel. 

Lets break it down into words using dplyr function unnest_tokens().

unnest_tokens() takes two parameters, first is the name of the resultant column and second is the name of source column which we want to unnest.

```{r}
# break the lines into words and store into dataframe as two_cities
two_cities<-two_cities%>%
  unnest_tokens(word,text)

two_cities[1:20,]
```

#### Sentiment Analysis

Now that we have all the words from the novel, lets evaluate the sentiments of those words. 

For that we can import a sentiment lexicon 'nrc' from tidytext package.

```{r}
two_cities$gutenberg_id<-NULL

# store all the sentiments into sent dataframe
sent<-get_sentiments('nrc')

# inner join of sent dataframe with two_cities 
# will give us the respective sentiments for each word

two_cities<-inner_join(two_cities,sent)
two_cities[1:10,]
```

#### Plotting

We have all the sentiments and words so lets plot the graph for the sentiments used in the novel using ggplot2.

```{r}
# group the words by the sentiments

two_cities<-two_cities%>%
  group_by(word)%>%
  summarize(freq=n(),sentiment=first(sentiment))
two_cities[1:10,]

# plotting graph
ggplot()+
  geom_bar(data=two_cities,aes(x=sentiment,y=freq)
           ,stat = 'identity',fill='red')


```


#### wordcloud

```{r}
wordcloud(two_cities$word,two_cities$freq,min.freq =50,
          colors = brewer.pal(6,'Dark2'),vfont=c("script","bold"))

```

