---
title: Graphs in R
author: ''
date: '2017-11-27'
slug: graphs-in-r
categories:
  - dplyr
  - ggplot2
tags: []
---

## *Let's start by importing the libraries we will need to plot a graph.*

## *We would need dplyr to do the data manipulations *

## *Lahman to get the data about all the baseball players for our plots*

## *And lastly, ggplot2 and ggiraph are needed for the graphs.*


```{r Importing Libraries into the environment, echo=TRUE, fig.align='center', message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(Lahman)
library(ggiraph)

```


## *Now that we have our libraries/packages, Let's do some data maipulation using dplyr*

## *We will search for all the players who have homeruns more than 400 in their careers.*

## *we will be using Batting table from Lahman package and grouping it by player_ids.*


```{r echo=TRUE, message=FALSE, warning=FALSE}
df<-Batting%>%
  group_by(playerID)%>%
  summarise(Career_HR = sum(HR), Career_SO=sum(SO))%>%
  filter(Career_HR>=400)

head(df)

```

## *As you can see we have playerID from our last query but we do not have names to identify our players.*
## *so lets join our dataframe with Master table and get the player names.*


```{r echo=TRUE, message=FALSE, warning=FALSE}

HR_VS_SO<-inner_join(df,Master,by=c("playerID"))%>%
  select(nameFirst,nameLast,Career_HR, Career_SO)


head(HR_VS_SO)


```


## *lets combine the first and last names into Name column.*


```{r echo=TRUE, message=FALSE, warning=FALSE}

HR_VS_SO$name<-paste(HR_VS_SO$nameFirst,HR_VS_SO$nameLast)

head(HR_VS_SO)


```


## *Now that we have all the needed data lets plot a graph of career Strikeouts vs career homeruns.*

## *NOTE : the tooltip doesnt work in the posts but it should work when you execute the query on your system.*

```{r echo=TRUE, fig.align='center', message=FALSE, warning=FALSE}

IntercGraph<-ggplot()+
  geom_point(data = HR_VS_SO,aes(x=Career_SO, y=Career_HR,tooltip=name,data_id=nameLast))+
  ggtitle("Career Homeruns vs. Strikeouts for Great Hitters")+
  xlab("Career Strikeout")+
  ylab("Career Homerun")

ggiraph(code =print(IntercGraph),hover_css = "fill:red;stroke:black")

```

## *Now lets try creating Bar graphs using the same package*


```{r, message=FALSE, warning=FALSE}

data1<-Teams%>%
  filter(yearID==1980)%>%
  select(teamID,HR)
  


```

```{r, message=FALSE, warning=FALSE}

ggplot()+
  geom_bar(data = data1 , aes(x=teamID,y=HR),stat = "identity",color="red",fill="blue")+
  coord_flip()


```


