---
title: Graphs in R
author: ''
date: '2017-11-27'
slug: graphs-in-r
categories:
  - dplyr
  - ggplot2
tags: []
---

# Creating Graphs

### Let's start by importing the libraries we will need to plot a graph.

### We would need dplyr to do the data manipulations 

### Lahman to get the data about all the baseball players for our plots

### And lastly, ggplot2 and ggiraph are needed for the graphs.


```{r Importing Libraries into the environment, echo=TRUE, fig.align='center', message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(Lahman)
library(ggiraph)

```


### Now that we have our libraries/packages, Let's do some data maipulation using dplyr

### We will search for all the players who have homeruns more than 400 in their careers.

### we will be using Batting table from Lahman package and grouping it by player_ids.


```{r echo=TRUE, message=FALSE, warning=FALSE}
df<-Batting%>%
  group_by(playerID)%>%
  summarise(Career_HR = sum(HR), Career_SO=sum(SO))%>%
  filter(Career_HR>=400)

head(df)

```

### As you can see we have playerID from our last query but we do not have names to identify our players.
### so lets join our dataframe with Master table and get the player names.


```{r echo=TRUE, message=FALSE, warning=FALSE}

HR_VS_SO<-inner_join(df,Master,by=c("playerID"))%>%
  select(nameFirst,nameLast,Career_HR, Career_SO)


head(HR_VS_SO)


```


### lets combine the first and last names into Name column.


```{r echo=TRUE, message=FALSE, warning=FALSE}

HR_VS_SO$name<-paste(HR_VS_SO$nameFirst,HR_VS_SO$nameLast)

head(HR_VS_SO)


```


### Now that we have all the needed data lets plot a graph.


```{r echo=TRUE, fig.align='center', message=FALSE, warning=FALSE}

IntercGraph<-ggplot()+
  geom_point(data = HR_VS_SO,aes(x=Career_SO, y=Career_HR))+
  ggtitle("Career Homeruns vs. Strikeouts for Great Hitters")+
  xlab("Career Strikeout")+
  ylab("Career Homerun")

ggiraph(code =print(IntercGraph),hover_css = "fill:red;stroke:black")

```